### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Results - Annealing XRD - added crystallization sources to table

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c }
		\toprule
		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
		& First Temp (\degree C) & Last Temp (\degree C) & First Temp (\degree C) & Last Temp (\degree C) \\
		\midrule
		Glass 						& 35 & 200 & 35 & 200 \\
		Mg$_{51}$Zn$_{20}$ 			& 170 & 200 & 140 & 200 \\
		Mg 							& 170 & 320 & 140 & 320 \\
		Ca$_{2}$Mg$_{5}$Zn$_{5}$	& 200 & 250 & 200 & 250 \\
		MgZn 						& 250 & 250 & 250 & 250 \\
		Ca$_{2}$Mg$_{5}$Zn$_{13}$ 	& 290 & 320 & 290 & 320 \\
		\bottomrule
	\end{tabular}
	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film.}
	\label{tab:Crystal_Sequence}
\end{table}

>>>>

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c }
		\toprule
		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
		& First Temp (\degree C) & Last Temp (\degree C) & First Temp (\degree C) & Last Temp (\degree C) \\
		\midrule
		Glass 						& 35 & 200 & 35 & 200 \\
		Mg$_{51}$Zn$_{20}$ \cite{Zhang2013, Khan1989} & 170 & 200 & 140 & 200 \\
		Mg 							& 170 & 320 & 140 & 320 \\
		Ca$_{2}$Mg$_{5}$Zn$_{5}$ \cite{Zhang2013, Cao2016} & 200 & 250 & 200 & 250 \\
		MgZn \cite{Khan1989} & 250 & 250 & 250 & 250 \\
		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013} & 290 & 320 & 290 & 320 \\
		\bottomrule
	\end{tabular}
	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film.}
	\label{tab:Crystal_Sequence}
\end{table}
